The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-08 author.tex
Normalise Heidelberg postal addresses

\author{F. Biscani}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}

@@

\author[0000-0002-8546-9128]{D. Homeier}
\affiliation{Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Landessternwarte, K{\"o}nigstuhl 12, D-69117 Heidelberg, Germany}

@@

\author[0000-0003-1585-225X]{P. H. Sladen}
\affiliation{ARI/ZAH, Heidelberg}

>>>>

\author{F. Biscani}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany}

@@

\author[0000-0002-8546-9128]{D. Homeier}
\affiliation{Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Landessternwarte, K{\"o}nigstuhl 12, 69117 Heidelberg, Germany}

@@

\author[0000-0003-1585-225X]{P. H. Sladen}
\affiliation{Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Astronomisches Rechen-Institut, M{\"o}nchhofstra{\ss}e 12--14, 69120 Heidelberg, Germany}
